\documentclass[12pt,letterpaper,onecolumn]{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage[super]{nth}

%\newcommand{\deg}{\(^\circ\)} 
\newcommand{\isotope}[2]{\(^{#1}\)#2}

\pagestyle{plain}

%\graphicspath{{./plots/}}

\title{Thesis Proposal}
\author{Steve Herrin}
%\date{}

\begin{document}
\maketitle
\setlength{\parskip}{9pt}

\section{Description}
The EXO-200 experiment is currently taking data in order to search for the neutrinoless double beta decay of \isotope{136}{Xe}. Currently, we have collected about twice as much data as we had when we published our first limit on this process, and the amount of data will continue to grow over the next few months, until we decide to publish. This should happen sometime in the latter half of 2012. I would like to write my thesis on those results.

I've already worked on many aspects that go into the analysis, so some chapters of my thesis should be straightforward to write. My muon tagging module does a good job at identifying muons passing through the TPC, as well as reconstructing their angles. I will have a chapter with descriptions of the algorithm, validation with Monte Carlo simulations, and results from EXO-200. Likewise, I've done extensive work improving the electron lifetime measurements in EXO-200, and so I can again describe my methods, simulations, and results. I can also write about my light map, which corrects for the varying light collection in EXO-200 as a function of position.

I'm continuing to work on signals and fitting, so there will be more to write about. I've been studying event topology as a way of reducing backgrounds, and can already say something about the usefulness. The metrics I've crated from event topology can be used to do a more sophisticated analysis than the simple single-site/multiple-site classification we've used in the past. Right now, my plan is to use these metrics to do an alternative analysis to the one that was done for the PRL paper. Combined with more data, improved efficiency, and an improved understanding of fiducial volume, this will hopefully lead to an improved limit.

EXO-200 also has not published anything on decays to excited states, Majoron emission, or solar axions. If the topology metrics prove less useful than they seem right now, or I run into other difficulties, I may decide to concentrate on these more exotic decays.

\newpage

\section{Outline}

\subsection{Physics Motivation}

\subsubsection{History and Theory of Neutrino Physics}
Neutrinos have mass. Oscillations. Current unknowns. Some theory.

\subsubsection{Neutrinoless Double Beta Decay}
Theory. Previous experiments, limits.

\subsection{EXO-200 Detector}

\subsubsection{Construction}
Wires, APDs, physical construction, WIPP

\subsubsection{Signals and Reconstruction}
Getting clusters from waveforms

\subsection{Electron Lifetime Correction}

\subsubsection{Description}
Attenuation due to electronegative impurities. How my correction works.

\subsubsection{Monte Carlo Simulations}
How well does my correction work on simulated data with known electron lifetime?

\subsubsection{Data and Results}
What's actually in the data. Pump flow correlation. How it improves resolution. Look at spatial and temporal variation.

\subsection{Light Map}

\subsubsection{Description}
Why a light map is needed. How I voxelize the detector. Any other corrections I apply on top of that.

\subsubsection{Data and Results}
What the light response look like. How it improves resolution.

\subsection{Muon Background Rejection}

\subsubsection{Algorithm}
Hough transforms, other cuts.

\subsubsection{Noise Tagger}
Why it's needed. How it works.

\subsubsection{Monte Carlo Simulations}
Efficiency in simulated data, and error on angle.

\subsubsection{Data and Results}
What we see in data. Muon rate, stopped muon rate, angular distribution.

\subsection{Event Topology}

\subsubsection{Method}
Describe using minimal spanning trees on energy depositions.

\subsubsection{Monte Carlo Simulations}
How well it works on simulated data.

\subsubsection{Data and Results}
What's actually in the data. Are certain backgrounds ruled out? Is there any information about the locations of backgrounds?

\subsection{Analysis}

\subsubsection{Describe Data}
When it was taken. Quality cuts.

\subsubsection{Describe Calibration}
When it was taken. What sources. How it's then applied to data.

\subsubsection{Overall Analysis Process}
Just an overview from raw waveforms to final spectrum. This includes anticorrelation.

\subsubsection{Systematics}
Things like fiducial volume and beta scale that can affect final results.

\subsubsection{PDF generation}
How we turn Monte Carlo simulations into something that can be compared to data.

\subsection{Fitting and Results}

\subsubsection{Maximum Likelihood analysis}
What method we apply to the spectrum to get fit results.

\subsubsection{Two Neutrino Measurement}
The result. Compare to previous measurements. Matrix elements.

\subsubsection{Zero Neutrino Limit(?)}
The result. Compare to previous measurements. Neutrino mass limit.

\subsubsection{Exotica Limits (Majoron, Solar Axion)(?)}
The result. Compare to other measurements. Cross-sections, couplings, etc.

\newpage

\section{Rough Schedule}
\begin{itemize}
\item \textit{\nth{1} half of October 2012} -- Write up muon and noise tagger. Descriptions, efficiencies, preliminary results.
\item \textit{\nth{2} half of October 2012} -- Write up electron lifetime correction. Description, preliminary results.
\item \textit{\nth{1} half of November 2012} -- Write up light map correction. Description, preliminary results.
\item \textit{\nth{2} half of November 2012} -- Write up topological background reduction. Description, preliminary results.
\item \textit{\nth{1} half of December 2012} -- Write about theory and EXO-200 detector
\item \textit{\nth{2} half of December 2012} -- Revisit previous topics and revise as needed. Decide whether to focus on \(0\nu\) or other exotica, and how much of a role these topology variables will play. 
\item \textit{\nth{1} half of January 2013} -- Start to write up analysis topics.
\item \textit{\nth{2} half of January 2013} -- Continue to write up analysis topics.
\item \textit{\nth{1} half of February 2013} -- Review what I've written. Write more about theory and EXO-200.
\item \textit{\nth{2} half of February 2013} -- Converge on final analysis results.
\item \textit{\nth{1} half of March 2013} -- Converge on final analysis results. Write up.
\item \textit{\nth{2} half of March 2013} -- Review everything, finish up theory and EXO-200 detector sections.
\item \textit{\nth{1} half of April 2013} -- Give draft to Marty to review. 
\item \textit{\nth{2} half of April 2013} -- Get feedback, incorporate suggestions.
\item \textit{\nth{1} half of May 2013} -- More drafts and reviewing. 
\item \textit{\nth{2} half of May 2013} -- Defend thesis.
\item \textit{June 2013} -- Knowledge transfer and graduate.
\end{itemize}

There are a couple unknowns in this schedule. I've allowed about two months for working on the results of the analysis. That's a reasonable amount of time, based on previous experience. Right now, it's unknown whether this will coincide with other efforts by the collaboration to write a paper.

\end{document}